---
title: "Basal Area"
date: "Generated: `r Sys.Date()`"
runtime: shiny
output:
    html_document:
        toc: true
        toc_depth: 3
        theme: spacelab
        highlight: zenburn
        number_sections: false
---

```{r global_opts, include=FALSE}

knitr::opts_chunk$set(fig.path="Figs/", echo=FALSE, warning=FALSE,
                      message=FALSE, dev='svg')

```

```{r setup}

source("R/setup.R", chdir=TRUE)

## DBH class breaks
## tp$breaks <- cut(tp$DBH, breaks=seq(5, max(tp$DBH, na.rm=TRUE)+5, by=5), include.lowest=TRUE)

```

# Subset
```{r subset}

source("R/subsetTransect.R", local=TRUE, chdir=TRUE)
uiOutput('transectChooser')
verbatimTextOutput('tSubText')


```

## Transects: barplots for DBH by size class
Trees with status == DEAD are removed.
Note: counts are not per unit area yet, what was the radius for regular transect plots (it's not entered in variable TRAD)?

```{r barplot_sizeclass}

source("R/barplotSizeClass.R", local=TRUE)

uiOutput('barSizeClassUI')
## uiOutput('tpSideTran')

```

## Permanent Plots: barplots stacked by species, split by years
Show area in each segment and the total area above each bar.  Ignore additional spruce.  Use only trees >= 5cm DBH to compare across years.

* Interactive options:
    - Subset: Plot, soil type
	- Labels: show or not?
	- Maybe better: two graphs, one line/species, one bars for totals

```{r pp_barplot}

pdat <- with(pp, pp[PPLOT == 4 & STAT=='ALIVE' & CLASS == 'P' & DBH >= 5 & BQUDX > 0 & BQUDX < 11 &
                    BQUDY > 0 & BQUDY < 11, ])

ba <- aggregate(BA ~ SPEC + YEAR, data=pdat, FUN=sum)

ggplot(ba, aes(x=YEAR, y=BA, fill = SPEC)) + geom_bar(stat='identity', color='black') + defaults +
  scale_fill_brewer(palette='Spectral')

```

```{r test}

source("R/subset.R", local=TRUE)
uiOutput("chooser")

```
